\documentclass{resume}

\begin{document}

% Heading
\begin{center}
  \textbf{\Large Salavat Dautov} \\
  \vspace{4pt}
  \small
  \faIcon{envelope}
  \href{mailto:dautovsalavatd@gmail.com}{\underline{dautovsalavat7@gmail.com}} $ $
  \faIcon{telegram}
  \href{https://t.me/sdautov}{\underline{sdautov}} $ $
  \faIcon{github}
  \href{https://github.com/sdautov}{\underline{sdautov}} $ $
  \faIcon{globe}
  \href{https://sdautov.github.io}{\underline{sdautov.github.io}}
\end{center}

% Education
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://eng.miet.ru/}{National Research University "Moscow Institute of Electronic Technology"}}{Moscow, Russia}
{Major: Informatics and Computer Engineering, Bachelor’s degree}{August 2018 – June 2022}
\resumeSubHeadingListEnd

% Work Experience
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://www.latera.ru/}{Latera LLC}}{Moscow, Russia}
{Software Developer}{March 2021 -- July 2022}
\resumeItemListStart
\resumeItemPlain{Contributed to the development of the billing system \href{https://hydra-billing.ru/}{Hydra} and an open-source application based on Camunda for automating business processes \href{https://hydra-oms.com/}{Hydra OMS.}}
\resumeItem{Gained experience}{
  \resumeItemListStart
  \resumeItemPlain{Writing integrations with payment systems.}
  \resumeItemPlain{Developing BPM on Camunda.}
  \resumeItemPlain{Developing packages, stored procedures, and functions in PL/SQL.}
  \resumeItemPlain{Optimizing and writing SQL queries.}
  \resumeItemPlain{Working with CI/CD.}
  \resumeItemPlain{Testing using Selenium.}
  \resumeItemPlain{Writing unit tests using PyTest Mock.}
  \resumeItemListEnd}
\resumeItem{Technologies used}{Oracle PL/SQL, Ruby on Rails, Bootstrap, Vue.js, Kotlin, React, memcached, Redis.}
\resumeItemListEnd
\resumeSubheading
{NPK Progress LLC}{Ufa, Russia}
{Engineer-Programmer}{July 2022 -- September 2022}
\resumeItemListStart
\resumeItemPlain{Participated in the improvement and support of information systems for the medical insurance fund of the Republic of Bashkortostan. Engaged in code refactoring, writing new functionality, and integration with the CryptoPro system.}
\resumeItem{Technologies used}{Oracle PL/SQL, C\#, ASP.NET Framework, ASP.NET Core, EntityFramework, MongoDB, RabbitMQ.}
\resumeItemListEnd
\resumeSubheading
{\href{https://www.nobilis.team/}{Nobilis.Team}}{Moscow, Russia}
{Software Developer}{September 2022 -- February 2024}
\resumeItemListStart
\resumeItemPlain{Involved in the development and support of a solution for accounting for natural resource use objects for Rosprirodnadzor, as well as in the migration from Salesforce CRM to BPMSoft solution for Philip Morris International. Engaged in the development of business processes, writing client-side application and server logic.}
\resumeItem{Technologies used}{Oracle, PostgreSQL, Microsoft SQL Server, C\#, ASP.NET Framework, ASP.NET Core, Redis.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Technical Skills
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{Programming Languages}{
  \resumeItemListStart
  \resumeItem{Commercial development experience with}{С\#, Ruby, Python, SQL, PL/SQL, JavaScript, TypeScript, Kotlin.}
  \resumeItem{Also have experience with}{С++ и Java.}
  \resumeItemPlain{Studying functional languages such as Haskell and Scala.}
  \resumeItemPlain{Proficient in HTML and CSS.} 
  \resumeItemListEnd}
\resumeItem{Frameworks, Libraries, and Technologies}{
  \resumeItemListStart
  \resumeItem{Backend}{ASP.NET, EntityFramework, Java EE, JDBC, Hibernate, Ruby on Rails, memcached, Redis.}
  \resumeItem{Frontend}{Vue.js (including experience migrating from Vue 2 to Vue 3), React, Bootstrap.}
  \resumeItemListEnd}
\resumeSubHeadingListEnd

% Languages
\section{Languages}
\resumeSubHeadingListStart
\resumeItem{Russian}{proficiency level -- native.}
\resumeItem{English}{proficiency level -- Intermediate (B1).}
\resumeSubHeadingListEnd

% Workflow
\section{Workflow}
\resumeSubHeadingListStart
\resumeItem{Experience with}{
  \resumeItemListStart
  \resumeItemPlain{Team development according to Scrum, Kanban, and Agile.}
  \resumeItemPlain{Regular code reviews.}
  \resumeItemPlain{Reviewing others' code.}
  \resumeItemPlain{Administration of servers on Windows Server, Linux.}
  \resumeItemPlain{Working with Docker and Kubernetes.}
  \resumeItemPlain{Migrating applications from Docker to Kubernetes.}
  \resumeItemPlain{Writing code documentation in Confluence.}
  \resumeItemListEnd}
\resumeItem{Able to work with}{
  \resumeItemListStart
  \resumeItemPlain{Version control systems such as git, SVN, Mercurial.}
  \resumeItemPlain{Bug tracking systems like Jira, YouTrack.}
  \resumeItemPlain{Continuous integration systems Bamboo, GitLab CI/CD, Jenkins.}
  \resumeItemPlain{Message brokers RabbitMQ, Kafka.}
  \resumeItemPlain{Relational databases Oracle, Microsoft SQL Server, PostgreSQL, MariaDB, MySQL, Firebird, SQLite.}
  \resumeItemPlain{NoSQL databases MongoDB, Redis, memcached.}
  \resumeItemPlain{Tools such as Swagger, Postman, Grafana, Kibana.}
  \resumeItemListEnd}
\resumeItem{Familiar with}{
  \resumeItemListStart
  \resumeItemPlain{Architectural patterns such as MVC, MVP, MVVM.}
  \resumeItemPlain{Various algorithms and data structures.}
  \resumeItemPlain{Many object-oriented design patterns.}
  \resumeItemPlain{Architectural styles REST, SOAP.}
  \resumeItemPlain{Development principles SOLID, DRY, KISS.}
  \resumeItemListEnd}
\resumeItem{Also have experience in development of}{
  \resumeItemListStart
  \resumeItemPlain{Android mobile applications (including using TensorFlow library).}
  \resumeItemPlain{Xamarin mobile applications.}
  \resumeItemPlain{Web applications for image recognition using CustomVision computer vision service.}
  \resumeItemPlain{Desktop applications using WPF, Swing, Qt.}
  \resumeItemPlain{Mobile games using Unity.}
  \resumeItemListEnd}
\resumeSubHeadingListEnd


% Internships
\section{Internships}
\resumeSubHeadingListStart
\resumeSubheadingShort
{\href{https://safeboard.kaspersky.ru/}{Kaspersky SafeBoard 2019}}{October 2019 – December 2019}
\resumeItemListStart
\resumeItemPlain{Trained in the development stream at the Kaspersky Lab. During the training, developed several web services on ASP.NET.}
\resumeItem{Technologies used}{Microsoft SQL Server, C\#, ASP.NET Framework, ASP.NET Core, EntityFramework, WPF.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Online Courses
\section{Online Courses}
\resumeSubHeadingListStart
\resumeSubheadingShort
{\href{https://ru.coursera.org/specializations/c-plus-plus-modern-development}{The Art of Modern C++ Development}}{September 2020 – February 2021}
\resumeItemListStart
\resumeItemPlain{Completed courses on C++ 17 development from MIPT and Yandex on Coursera.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Events
\section{Events}
\resumeSubHeadingListStart
\resumeItem{Participated in various competitions and hackathons, including}{
  \resumeItemListStart
  \resumeItemPlain{ACM ICPC 2016.}
  \resumeItemPlain{ICPC 2018.}
  \resumeItemPlain{\href{https://microsoft-student-partner.timepad.ru/event/923680/}{Microsoft Student Partners Game Hack 2019} (our team received the audience choice award).}
  \resumeItemPlain{\href{https://it-mai.timepad.ru/event/934116/}{MAI C\# hackathon 2019} (team hackathon, where our team took first place).}
  \resumeItemPlain{ICPC 2019.}
  \resumeItemPlain{\href{https://hack.moscow/}{Hack Moscow 2019}.}
  \resumeItemPlain{Kaspersky SafeBoard 2019 Hackathon (individual hackathon as the final stage of selection).}
  \resumeItemListEnd}
\resumeSubHeadingListEnd

% About Me
\section{About Me}
\resumeSubHeadingListStart
\resumeItemPlain{In 2022, I successfully graduated from the National Research University “Moscow Institute of Electronic Technology” with a degree in Informatics and Computer Engineering. During my studies, I gained practical experience in programming single-board computers and microcontrollers based on the ARM architecture. As part of my coursework, I implemented a processor based on the RISC-V architecture using Verilog. I also developed an “on-chip system,” which gave me the opportunity to gain experience working with various interfaces such as VGA, PS/2, USB I2C, and SPI.}
\resumeSubHeadingListEnd
\end{document}
